Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-07-23 analysis/report/effectiveness_report.Rmd
improve axes

```{r, curves, echo=FALSE, message=FALSE, warning=FALSE, out.width='90%'}

@@

  effects_plot <-
    ggplot(data = effects) +
    geom_point(aes(y=estimate, x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_linerange(aes(ymin=conf.low, ymax=conf.high, x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_hline(aes(yintercept=1), colour='grey')+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(breaks=unique(effects$term_left), limits=c(min(effects$term_left), max(effects$term_right)+1), expand = c(0, 0))+
    scale_y_log10(
    breaks=c(0.1, 0.25, 0.33, 0.5, 0.75, 1, 1.33, 2, 3, 4, 10)
    #sec.axis = dup_axis(name="favours\n<- BNT162b2 / ChAdOx1 ->", breaks = NULL)
  )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=2))+
    labs(
      y="Hazard ratio\nChAdOx1 / BNT162b2",
      x="Days since vaccination",
      colour=NULL
     ) +
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  # 
  # calendar_plot <- read_rds(here("output", outcome, "calendar", glue("effect_plot.rds"))) + 
  #   labs(title=NULL)+
  #   coord_cartesian(ylim=c(0.25,4))+
  #   theme(text = element_text(size=10))
  # 
  # timesincevax_plot <- read_rds(here("output", outcome, "timesincevax", glue("effect_plot.rds"))) + 
  #   labs(title=NULL)+
  #   coord_cartesian(ylim=c(0.25,4))+
  #   theme(text = element_text(size=10))
  # 
  cat(glue("### {outcome_descr}"), "  \n")

  #effects_plot <- wrap_plots(calendar_plot, timesincevax_plot, nrow=1)#, guides='collect')

  wrap_plots(
   km_plot,
   effects_plot,
   ncol=1
  ) +
  plot_annotation(title = outcome_descr)

>>>>

```{r, curves, echo=FALSE, message=FALSE, warning=FALSE, out.width='90%', results='asis'}

@@

  effects_plot <-
    ggplot(data = effects) +
    geom_point(aes(y=estimate, x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_linerange(aes(ymin=conf.low, ymax=conf.high, x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_hline(aes(yintercept=1), colour='grey')+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(breaks=unique(effects$term_left), limits=c(min(effects$term_left), max(effects$term_right)+1), expand = c(0, 0))+
    scale_y_log10(
    breaks=c(0.1, 0.125, 0.25, 0.33, 0.5, 0.75, 1, 1.33, 2, 3, 4, 8,10),
    sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
  )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=2))+
    labs(
      y="Hazard ratio",#\nChAdOx1 / BNT162b2",
      x="Days since vaccination",
      colour=NULL
     ) +
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  # 
  # calendar_plot <- read_rds(here("output", outcome, "calendar", glue("effect_plot.rds"))) + 
  #   labs(title=NULL)+
  #   coord_cartesian(ylim=c(0.25,4))+
  #   theme(text = element_text(size=10))
  # 
  # timesincevax_plot <- read_rds(here("output", outcome, "timesincevax", glue("effect_plot.rds"))) + 
  #   labs(title=NULL)+
  #   coord_cartesian(ylim=c(0.25,4))+
  #   theme(text = element_text(size=10))
  # 
  #cat(glue("### {outcome_descr}"), "  \n")

  #effects_plot <- wrap_plots(calendar_plot, timesincevax_plot, nrow=1)#, guides='collect')
  cat("  \n\n")
  print(glue("### {outcome_descr}"), "  \n")
  print(km_plot)
  print(effects_plot)
  cat("  \n\n")
  # wrap_plots(
  #  km_plot + labs(title=outcome_descr),
  #  effects_plot,
  #  ncol=1
  # ) +
  # plot_annotation(title = outcome_descr)
